quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-22 paper-quollr.tex
Change buffer_x and buffer_y defaults to have one more bin along x and y (need to experiment with some other data sets to set up the default)

\begin{verbatim}
#> [1] 4
\end{verbatim}

@@

\begin{verbatim}
#> [1] 7
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 28
#> Columns: 2
#> $ x <dbl> -0.1732051, 0.1732051, 0.5196152, 0.8660254, 0.0000000, 0.3464102, 0~
#> $ y <dbl> -0.15, -0.15, -0.15, -0.15, 0.15, 0.15, 0.15, 0.15, 0.45, 0.45, 0.45~
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 168
#> Columns: 6
#> $ c_x   <dbl> -0.1732051, -0.1732051, -0.1732051, -0.1732051, -0.1732051, -0.1~
#> $ c_y   <dbl> -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -~
#> $ x     <dbl> 0.0000000, 0.0000000, -0.1732051, -0.3464102, -0.3464102, -0.173~
#> $ y     <dbl> -0.05040708, -0.24959292, -0.34918584, -0.24959292, -0.05040708,~
#> $ id    <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
#> $ hexID <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
\end{verbatim}

@@

\begin{verbatim}
#>            x     y hexID std_counts
#> 1  0.1732051 -0.15     2  0.2352941
#> 2  0.0000000  0.15     5  0.5294118
#> 3  0.3464102  0.15     6  0.4117647
#> 4  0.1732051  0.45    10  0.1764706
#> 5  0.5196152  0.45    11  0.3529412
#> 6  0.6928203  0.75    15  0.7058824
#> 7  0.8660254  1.05    20  0.4705882
#> 8  0.6928203  1.35    23  0.2941176
#> 9  1.0392305  1.35    24  0.2352941
#> 10 0.8660254  1.65    28  1.0000000
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 75
#> Columns: 4
#> $ pred_UMAP_1 <dbl> 0.1732051, 0.6928203, 0.8660254, 0.1732051, 0.1732051, 0.8~
#> $ pred_UMAP_2 <dbl> 0.45, 0.75, 1.05, -0.15, 0.45, 1.65, 0.75, 0.75, 0.75, 1.6~
#> $ ID          <int> 1, 2, 3, 4, 6, 7, 8, 9, 11, 12, 14, 15, 16, 17, 19, 20, 21~
#> $ pred_hb_id  <int> 10, 15, 20, 2, 10, 28, 15, 15, 15, 28, 15, 10, 24, 5, 15, ~
\end{verbatim}

>>>>

\begin{verbatim}
#> [1] 5
\end{verbatim}

@@

\begin{verbatim}
#> [1] 8
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 40
#> Columns: 2
#> $ x <dbl> -0.1732051, 0.1732051, 0.5196152, 0.8660254, 1.2124356, 0.0000000, 0~
#> $ y <dbl> -0.15, -0.15, -0.15, -0.15, -0.15, 0.15, 0.15, 0.15, 0.15, 0.15, 0.4~
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 240
#> Columns: 6
#> $ c_x   <dbl> -0.1732051, -0.1732051, -0.1732051, -0.1732051, -0.1732051, -0.1~
#> $ c_y   <dbl> -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -~
#> $ x     <dbl> 0.0000000, 0.0000000, -0.1732051, -0.3464102, -0.3464102, -0.173~
#> $ y     <dbl> -0.05040708, -0.24959292, -0.34918584, -0.24959292, -0.05040708,~
#> $ id    <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
#> $ hexID <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
\end{verbatim}

@@

\begin{verbatim}
#>            x     y hexID std_counts
#> 1  0.1732051 -0.15     2  0.2352941
#> 2  0.0000000  0.15     6  0.5294118
#> 3  0.3464102  0.15     7  0.4117647
#> 4  0.1732051  0.45    12  0.1764706
#> 5  0.5196152  0.45    13  0.3529412
#> 6  0.6928203  0.75    18  0.7058824
#> 7  0.8660254  1.05    24  0.4705882
#> 8  0.6928203  1.35    28  0.2941176
#> 9  1.0392305  1.35    29  0.2352941
#> 10 0.8660254  1.65    34  1.0000000
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 75
#> Columns: 4
#> $ pred_UMAP_1 <dbl> 0.1732051, 0.6928203, 0.8660254, 0.1732051, 0.1732051, 0.8~
#> $ pred_UMAP_2 <dbl> 0.45, 0.75, 1.05, -0.15, 0.45, 1.65, 0.75, 0.75, 0.75, 1.6~
#> $ ID          <int> 1, 2, 3, 4, 6, 7, 8, 9, 11, 12, 14, 15, 16, 17, 19, 20, 21~
#> $ pred_hb_id  <int> 12, 18, 24, 2, 12, 34, 18, 18, 18, 34, 18, 12, 29, 6, 18, ~
\end{verbatim}
